Data Specialization for a Staged Lambda Calculus

### 2015-02-11 paper/figures/splitting-overview.tex
Fixed up the evaluation summary figure

\begin{figure*}
\textbf{Languages:}
\begin{itemize}
\item \lang: two-staged typed lambda calculus with product, sum, and
  recursive types
\item \langTwo: monostaged typed lambda calculus
\item \langmono: an unstaged lambda calculus
\end{itemize}

\textbf{\lang\ Dynamic Semantics (\ref{sec:semantics})}
\begin{itemize}
\item 
\bbone-Evaluation: $e\mathbin{\redonesym}[\xi;v]$, where $\xi$ is a \emph{residual table} and $v$ is a \emph{partial value}.

\item
Residualization: $e\mathbin{\redtwosym}q$, where $q$ is a \emph{residual} in the unstaged language \langTwo

\item 
Table reification: $[\xi;q]\mathbin{\reifysym} q'$, where $q,q'$ are residuals,
$\xi$ is a residual table.

\item
Residual evaluation: $q\mathbin{\redsym} v$, where $q$ is a residual, $v$ is a
value.
\end{itemize}

\caption{Summary of \lang\ evaluation.}
\label{fig:dynamicsSummary}
\end{figure*}

>>>>

\begin{figure}
\begin{abstrsyn}

\textbf{Monostage Evaluation (also used for \bbone-Evaluation at \bbonep):}

\hspace{2em} Evaluation Form: $\reduce e v$, where

	\hspace{4em} $e$ is the monostage term to be evaluated

	\hspace{4em} $v$ is the resulting value

\textbf{\bbone-Evaluation at \bbonem:}

\hspace{2em} Evaluation Form (Evaluation): $\diaone e {\xi;v}$, where

	\hspace{4em} $e$ is the term at world \bbonem\ to be evaluated

	\hspace{4em} $\xi$ is the resulting residual table

	\hspace{4em} $v$ is the resulting partial value

\textbf{\bbone-Evaluation at \bbtwo:}

\hspace{2em} Evaluation Form (Residualization): $\diatwo e q$, where

	\hspace{4em} $e$ is the term at world \bbtwo\ to be evaluated

	\hspace{4em} $q$ is the resulting residual

\hspace{2em} Auxiliary Judgement (Reification): $\reify \xi q q'$, where

	\hspace{4em} $\xi$ is the residual table to be reified into \texttt{let} terms

	\hspace{4em} $q$ is a residual to be placed at the bottom of the \texttt{let}s

	\hspace{4em} $q'$ is the resulting residual

\end{abstrsyn}
\caption{Summary of \lang\ evaluation.}
\label{fig:dynamicsSummary}
\end{figure}
